Lattice Boltzmann study of mass transfer for two-dimensional Bretherton/Taylor bubble train flow

### 2012-07-23 Text/introduction.tex
Add acknowledgements.

\section{Summary}
This work examines a way to calculate the volumetric mass transfer coefficient in the framework of
the lattice Boltzmann method. Overall, the easiest recipe is to perform simulations 
with periodic boundary conditions
and calculate the volumetric mass transfer coefficient based on the
domain-averaged concentration through any formulation (\citeauthor{vanbaten-circular}, periodic boundary conditions, simulations of several unit cells) as they produce consistent results. The best accuracy
is achieved with formulations based on the mass difference or on the averaged domain concentrations
taken in different times, Eq. \ref{theor:continuous:mass:transfer}. Eq.
\ref{theor:average:concentration:time} gives a slightly overestimated volumetric mass transfer
coefficients (less than $10\%$). The original formulation of
\citet{vanbaten-circular} is inconsistent if one takes the inlet/outlet flux-averaged concentration
to be the characteristic concentration. Simulations of several unit cells are harder to perform, but they
indicate how well the liquid slug is mixed.  For velocity patterns of $Ca\geq
0.7$ simulations with a few unit cells allow to calculate the volumetric mass transfer
coefficient based on the spatial location only, without requiring the time snapshots of domain concentration values used in all other
approaches. Finally, a sample of results was
compared with the experimental correlation of \citet{yue-mass} and shown to be in good agreement. 

>>>>

\section{Summary}
This work examines a way to calculate the volumetric mass transfer coefficient in the framework of
the lattice Boltzmann method. Overall, the easiest recipe is to perform simulations 
with periodic boundary conditions
and calculate the volumetric mass transfer coefficient based on the
domain-averaged concentration through any formulation (\citeauthor{vanbaten-circular}, periodic boundary conditions, simulations of several unit cells) as they produce consistent results. The best accuracy
is achieved with formulations based on the mass difference or on the averaged domain concentrations
taken in different times, Eq. \ref{theor:continuous:mass:transfer}. Eq.
\ref{theor:average:concentration:time} gives a slightly overestimated volumetric mass transfer
coefficients (less than $10\%$). The original formulation of
\citet{vanbaten-circular} is inconsistent if one takes the inlet/outlet flux-averaged concentration
to be the characteristic concentration. Simulations of several unit cells are harder to perform, but they
indicate how well the liquid slug is mixed.  For velocity patterns of $Ca\geq
0.7$ simulations with a few unit cells allow to calculate the volumetric mass transfer
coefficient based on the spatial location only, without requiring the time snapshots of domain concentration values used in all other
approaches. Finally, a sample of results was
compared with the experimental correlation of \citet{yue-mass} and shown to be in good agreement.

\section{Acknowledgements}
M.J. acknowledges a scholarship from the TWING project co-financed by the European Social Fund.
